Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-27 analysis/paper/sim_survey_paper.Rmd
Finish drafting paper!

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to be uniformly distributed within a cell when, in the real-world, there are likely finer-scale aggregations. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. This is a short, non-inclusive, list of additional variability that likely occurs in the real-world but was not implemented here for simplicity.

@@

Using an age-length key in conjunction with the length distribution to estimate the age distribution is standard procedure in the analysis of fisheries-independent survey data as only a small fraction of the catch is typically aged. This is because the aging procedure is costly and time-consuming whereas length measurements are relatively easy to obtain. Ages are generally determined from length-stratified sub-samples of the catch and raw proportions of age-at-length are used to assign ages to fish in specific length groups. Age-length keys are rarely stratified due to a small number of samples and, as such, they are usually constructed at larger spatial scales. Here we construct one age-length key for the division, as is done for the analysis of 3Ps cod. There is, however, a potential cost to the spatial scale of the key. Namely, it is unlikely that one age-length key is representative for the whole region because the probability of being a specific age given length varies in space [@Berg2012]. This would not be an issue if there was no age-specific clustering, but this seems unlikely given the common observation that fish caught together tend to be more similar than those in the general population [@Pennington1994; @Pennington2002; @Stewart2014]. Because different age groups sometimes occur in different places, the translation of lengths to ages may be biased by the samples used to generate the age-length key. This bias is perhaps compounded by the length-stratified sampling of ages such that the ages sampled may be skewed towards sets with the most catch, especially under scenarios where length sampling effort is high. If this is the case, then the representativeness of the age-length key to the whole population could be deminished by excessive length sampling.

Requires further research. Solutions to the problem... (e.g. berge and kristensen).

### TODO

- Look into the ictopelagic sampling design literature (suggestion from Pierre)
- Look into work done on occupancy modeling and sampling design for such studies (i.e. book suggestion by Aaron)

@@

- Feedback and advice: Aaron Adamack, Alejandro Buren, Noel Cadigan, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Derek Osborne, Pierre Pepin, Dwayne Pittman, Don Power, Greg Robertson, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Dave Cote for a review of a previous version of this manuscript

>>>>

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell when, in the real-world, they may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. This is a short, non-inclusive, list of additional variability that likely occurs in the real-world but was not implemented here for simplicity.

@@

Using an age-length key in conjunction with the length distribution to estimate abundance at age is standard procedure in the analysis of fisheries-independent survey data as only a small fraction of the catch is typically aged. This is because the aging procedure is costly and time-consuming whereas length measurements are relatively easy to obtain. Ages are generally determined from length-stratified sub-samples of the catch and raw proportions of age-at-length are used to assign ages to fish in specific length groups. Age-length keys are usually constructed at larger spatial scales because there are rarely enough samples to stratify these data. Here we construct one age-length key for the division, as is done for the analysis of 3Ps cod. There is, however, a potential cost to the spatial scale of the key. Namely, it is unlikely that one age-length key is representative for the whole region because the probability of being a specific age given length varies in space [@Berg2012]. This would not be an issue if there was no size (age) specific clustering, however, this may not always be the case because different size groups often occur in different places because of ontogenetic habitat shifts [@dahlgren2000; @galaiduk2017]. For instance, it is not uncommon for populations to form distinct nursery and spawning areas [@marteinsdottir2000; @booth2000]. Because different age groups sometimes occur in different places, the translation of lengths to ages may be biased by the samples used to generate the age-length key. This bias is perhaps compounded by the length-stratified sampling of ages such that the ages sampled may be skewed towards sets with the most catch, especially under scenarios where length sampling effort is high. If this is the case, then the representativeness of the age-length key to the whole population could be diminished by excessive length sampling.

The negative consequences of excessive length sampling on abundance at age estimates are most apparent under the low set density scenarios. The precision of the estimates are also the poorest when fewer sets are conducted. Sets, however, are the most costly sample to obtain and, as such, the set densities of fisheries-independent surveys tend to be on the lower end of the scenarios presented in this paper. The set density of the multi-species survey conducted by Fisheries and Oceans Canada in the Newfoundland region, for instance, ranges between 0.001 and 0.002 sets / km^2^. Length sampling effort, in contrast, tends to be on the higher end of the scenarios presented here because lengths are relatively cheap and easy to obtain. Again, using Fisheries and Oceans Canada sampling protocol from the Newfoundland region as an example, it is not uncommon for length sampling effort to be capped at 500 measurements per set. The results presented in this paper paradoxically suggest that better abundance at age estimates are obtained by lowering the length sampling cap. Results also indicate that reductions to length sampling effort would not significantly impact abundance at length estimates. Nonetheless, it is hard to be prescriptive because this simulation is far from a perfect reflection of reality and it focuses on one case study. Further research is required on the consequences of some of the assumptions of this simulation as well as the interaction between age-specific clustering, length-stratified sampling and the age-length key. Ideally, the simulation would also include multiple species with different life-histories and distributions, and also integrate a cost component to assess the trade-offs between information and cost. Finally, it would be interesting to test alternate analyses of these data that may account for the spatial structure of the age-length key [e.g. @Berg2012].

While much work has yet to be done, results from the simple simulation echo the growing body of literature which concludes that extra sub-sampling is an ineffective means of improving estimates relative to sampling more locations [@Pennington1994; @Pennington2002; @Stewart2014; @Bogstad1995; @Coggins2013; @Zhang2013]. In general, the most significant source of variation in fisheries-independent surveys stems from set-to-set variation, and not variability from individual sub-samples. This is largely because fish caught together tend to be more similar than those in the general population [@Pennington1994]. Therefore, if the goal of a trawl survey is to maximize information, it is likely better to stop collecting psudoreplicates and, instead, focus efforts on other species or the next set.

@@

- Feedback and advice: Aaron Adamack, Alejandro Buren, Noel Cadigan, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Derek Osborne, Pierre Pepin, Dwayne Pittman, Don Power, Greg Robertson, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Dave Cote for a review of a previous version of this manuscript
- NSERC visiting-fellow program
